%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Mohamed Rehan} \\ \vspace{2pt}
    \small  +966557876404 $|$ \href{mailto:mohamedrehan54321@gmail.com}{\underline{mohamedrehan54321@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/mohamed-rehan/}{\underline{linkedin.com/in/mohamed-rehan}} $|$
    \href{https://www.github.com/mohamedrehan1}{\underline{github.com/mohamedrehan1}}
\end{center}

%-----------SUMMARY-----------

\section{Summary}
\resumeSubHeadingListStart
  \item
    \small{Detail-oriented and creative Frontend Engineer with 1+ year of experience building responsive, user-friendly web applications. Passionate about writing clean, maintainable code and continuously learning to stay current with industry trends. Collaborative team player with a focus on delivering impactful user experiences.}
\resumeSubHeadingListEnd

%-------------------------------------------


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{:  TypeScript, JavaScript, Rust (beginner)} \\
     \textbf{Frontend}{: React.js, Next.js, HTML, CSS, Tailwind CSS, shadcn/ui, Redux} \\
    \textbf{Backend}{: Node.js, Express, MongoDB, Prisma (ORM)} \\
     \textbf{DevOps}{: Docker, Docker Swarm} \\
     \textbf{Others}{: Git}
    }}
 \end{itemize}


%-------------------------------------------

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Frontend Engineer}{Feb 2025 -- Present}
      {MRNWARE}{Remote, Egypt}
      \resumeItemListStart
        \resumeItem{Developed a car rental software platform to streamline vehicle rental operations.}
        \resumeItem{Create reporting and analytics dashboards, enabling clients to monitor key metrics like fleet 
utilization and revenue, which improved decision-making and operational efficiency. }
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

     \resumeSubheading
      {Frontend Engineer}{Aug 2023 -- Oct 2023}
      {TG4T}{Remote, United Arab Emirates}
      \resumeItemListStart
        \resumeItem{Collaborated with backend team for seamless integration.}
        \resumeItem{Optimize web applications for maximum speed and scalability.}
      \resumeItemListEnd

    \resumeSubheading
      {Frontend Engineer}{Jul 2022 -- Dec 2022}
      {Mighty Operators}{Remote, United Arab Emirates}
      \resumeItemListStart
        \resumeItem{Converted legacy Active Directory consoles into a modern, responsive web application.}
        \resumeItem{Developed component-based interfaces that provided a seamless user experience.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------CONTRIBUTIONS-----------
\section{Contributions}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Open Source Contributor}{Dec 2024 -- Jan 2025}
      {\href{https://github.com/PalisadoesFoundation/talawa-admin}{{PalisadoesFoundation/talawa-admin}}}{Remote, Github}
      \resumeItemListStart
        \resumeItem{ Contributed to the \href{https://github.com/PalisadoesFoundation/talawa-admin/pull/3112}{\underline{OrgPeopleListCard}} component by writing unit tests, enhancing error handling, 
and collaborating with contributors to improve functionality. (React, TypeScript, Jest, Apollo Client). }
        \resumeItem{Refactored CSS for \href{https://github.com/PalisadoesFoundation/talawa-admin/pull/2993} {\underline{EventStatistics}} component, improving code maintainability and ensuring 
consistent styling.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{HomeAway} $|$ \emph{Next.js , Prisma, Clerk}}{}
          \resumeItemListStart
            \resumeItem{Built an application that allows users to book properties, manage reservations, and 
create profiles. \href{https://github.com/mohamedrehan1/home-away}{\underline{Github}}}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Ecommerce Website } $|$ \emph{React.js}}{}
          \resumeItemListStart
            \resumeItem{Implemented key features such as product listing, search and filter, product detail pages, cart management, and a checkout flow. \href{https://github.com/mohamedrehan1/Ecommerce-Website}{\underline{Github}}}
          \resumeItemListEnd

          \resumeProjectHeading
          {\textbf{Natours} $|$ \emph{Node.js, Express, MongoDB, Mongoose, Pug.js}}{}
          \resumeItemListStart
            \resumeItem{Developed a server-side rendered tour booking application using the MVC architecture, with a strong focus on performance and security measures such as rate limiting and data sanitization. \href{https://github.com/mohamedrehan1/natours}{\underline{Github}}}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Certificates-----------
\section{Certificates}
    \resumeSubHeadingListStart    
        \resumeSubheading
      {Front End Web Development Professional Nanodegree}{Aug 2021 -- Nov 2021}
      {Udacity}{}
      \resumeItemListStart
        \resumeItem{Completed the Front End Web Development Nanodegree from Udacity, gaining hands-on experience in building responsive, interactive web applications. \href{https://www.udacity.com/certificate/XLTGAKSF}{\underline{Link}}}

      \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor's degree in Electronics and Communication Engineering}{Kafr El-Sheikh, Egypt}
      {Faculty of Engineering Kafr El-Sheikh University}{2018 -- 2023}
  \resumeSubHeadingListEnd


\end{document}
